\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc} % pentru caractere speciale și textendash
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\definecolor{gray}{gray}{0.3}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}

% Configurare globală pentru liste de tip itemize (bullets)
\setlist[itemize]{
  topsep=1pt,
  itemsep=1pt,
  parsep=0pt,
  partopsep=0pt,
  leftmargin=1.5em,
  label=\textendash % liniuță elegantă
}

\pagestyle{empty}

% Stiluri pentru titluri de secțiuni
\titleformat{\section}{\large\bfseries\uppercase}{\thesection}{1em}{}
\titleformat{\subsection}[runin]{\bfseries}{}{0pt}{}[---]

% Spațiere între secțiuni
\titlespacing{\section}{0pt}{10pt}{5pt}
\titlespacing{\subsection}{0pt}{6pt}{2pt}

% Linie subțire personalizată
\newcommand{\myrule}{\noindent\rule{\linewidth}{0.4pt}}

\begin{document}

% NUME MARE CENTRAT
\begin{center}
    {\LARGE \textbf{AURELIAN-ANDREI PANAIT}}\\
    \vspace{0.2cm}
    Arr 14, 17 Rue Deparcieux, Paris 75014, France\\
    \href{mailto:aurelian-andrei.panait@etu.minesparis.psl.eu}{Email} $\diamond$ 
    \href{https://aurelianpanait.github.io}{Personal website} $\diamond$
    \href{https://www.linkedin.com/in/panait-andrei-52b598100/}{LinkedIn}
\end{center}

\section*{PERSONAL PROFILE}
\textbf{MSc student in Energy at \href{https://www.minesparis.psl.eu} {Mines Paris – PSL}} and former \textbf{Proprietary Trading Intern – Energy Markets at \href{https://tinmar.ro/en/} {Tinmar Energy}}. Passionate about solving real-world problems through the intersection of energy systems, trading, data analysis, and programming. Obtained my BSc in Energy Engineering from\href{https://upb.ro/}{ Politehnica University of Bucharest}.

\myrule

\section*{PREVIOUS PROFESSIONAL EXPERIENCE}
\myrule

\textcolor{violet}{\textbf{Proprietary Trading Intern}---Tinmar Energy} \hfill \textit{July 2024 – October 2024} \\[-2.0ex]
\begin{itemize}
    \item Executed proprietary trades in the German and Central \& South-Eastern European (CSEE) power markets based on market fundamentals, demand forecasts, and short-term price models.
    \item Developed short- and long-term price forecasting models for electricity, gas, and emission derivatives.
    \item Collaborated with senior traders on strategy optimization and risk mitigation.
    \item Utilized EEX, ICE, and OPCOM platforms for position monitoring and market execution.
\end{itemize}

\vspace{0.3cm}

\textcolor{violet}{\textbf{Energy Trading Analyst Intern}---Tinmar Energy} \hfill \textit{June 2023 – October 2023} \\[-2.0ex]
\begin{itemize}
    \item Analyzed energy consumption patterns and developed demand forecasting models using Python.
    \item Handled BRP notifications and ensured compliance with TSO reporting obligations.
    \item Monitored day-ahead and intraday markets on OPCOM and assessed short-term volatility risks.
    \item Automated internal reporting tools in Excel (incl. VBA) and created visual dashboards in Power BI.
\end{itemize}

\vspace{0.3cm}

\textcolor{violet}{\textbf{Optical Technology Engineer}---Spectro Optica Serv. SRL} \hfill \textit{March 2020 – June 2023} \\[-2.0ex]
\begin{itemize}
    \item Maintained and optimized optical engineering equipment for diagnostic and industrial use.
    \item Performed calibration procedures and developed maintenance protocols.
    \item Ensured high standards in optical performance and engineering precision.
\end{itemize}

\section*{\textcolor{gray}{EDUCATION}}
\myrule

\textcolor{violet}{\textbf{Master's in Energy}---MINES Paris – PSL, Paris, France} \hfill \textit{February  2025 – Present} \\[-3.0ex]
\vspace{0.5ex}
\begin{itemize}
  \item Specialization: Renewable Energy Integration \& Energy Efficiency.
  \item Core modules: Data Processing, Python, Basics of Nuclear Energy, Heat and Mass Transfer, Fluid Mechanics, Solid-State Electronics.
\end{itemize}

\vspace{0.4cm}

\textbf{\textcolor{violet}{National University of Science and Technology POLITEHNICA, Bucharest}} \\[-2.0ex]


\begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}X r@{}}
MSc in Computational Modeling for Renewable Energy  (10/2024–02/2025) & \textit{\textcolor{gray}{Merit Scoalrship, Grade 94\%}} \\
Bachelor’s in Energy Engineering (09/2020–07/2024) & \textit{\textcolor{gray}{First Class}} \\
\multicolumn{2}{@{}l}{\textit{\textcolor{gray}{Thesis: Solar Energy Modeling for Floating Photovoltaic Systems on Inland Reservoirs}}} \\
\multicolumn{2}{@{}l}{\textit{\textcolor{gray}{Advisor:Liana Ioana Vuta}}} \\

\end{tabularx}





\vspace{0.4cm}



\textbf{\textcolor{violet}{The University of Manchester, UK}} \\[-2.0ex]


\begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}X r@{}}
Undergraduate Studies in Electronic Engineering  (09/2015–07/2016) & \textit{\textcolor{gray}{Merit Scoalrship}} \\

\end{tabularx}

\vspace{0.4cm}

\textbf{\textcolor{violet}{Tudor Vianu National High School of Computer Science, Bucharest Romania}} \\[-2.0ex]


\begin{tabularx}{\linewidth}{@{}>{\raggedright\arraybackslash}X r@{}}
  Computer Science and Mathematics (09/2011–05/2015) & \textit{\textcolor{gray}{Grade 90.5\%}} \\

\end{tabularx}

\newpage

\section*{\textcolor{gray}{PROFESSIONAL SKILLS}}
\myrule
\vspace{1ex}
\textbf{\textcolor{violet}{Programming Languages}} 
\begin{itemize}
  \item Python (since ’15), MATLAB, VBA.
  
\end{itemize}

\vspace{0.5ex}

\textbf{\textcolor{violet}{Technical Skills}} \\[-3.0ex]
\begin{itemize}
  \item Data Analysis · Solar Resource Modeling · Differential Equations · Linear Algebra 
\end{itemize}

\vspace{0.1cm}

\section*{\textcolor{gray}{PERSONAL PROJECTS}}
\myrule

\textbf{\textcolor{violet}{Covered Call Trading Tool – Python}} \hfill \textit{Jan 2025} \\[-3.0ex]
\begin{itemize}
  \item Built a personal tool to evaluate covered call strategies using the Black-Scholes model.
  \item Computes option pricing, delta, breakeven point, and P\&L analysis.
  \item Developed in Python using \texttt{NumPy}, \texttt{Pandas}, and \texttt{Matplotlib}.
\end{itemize}

\vspace{0.1cm}


\textbf{\textcolor{violet}{ Solar Irradiance Modeling and Site Suitability Tool}} \hfill \textit{\href{https://github.com/aurelianpanait/Solar-Energy-Modeling-for-Floating-Photovoltaic-Systems-on-Inland-Reservoirs}{Code}} \\[-3.0ex]
\begin{itemize}
  \item Developed a custom Python implementation of the Sukhatme-Nayak tilted irradiance model to convert NASA POWER GHI data into TGI for multiple Romanian reservoirs. The algorithm calculated beam, diffuse, and reflected irradiance components using solar geometry equations (declination, sunset hour angle, clearness index, etc.). Conducted spatial and statistical analysis to identify high-potential sites for floating PV deployment, integrating environmental and technical criteria.
  
\end{itemize}

\vspace{0.1cm}

\section*{\textcolor{gray}{INTERESTS}}
\myrule

\textbf{\textcolor{violet}{Languages}} \\[-3.0ex]
\begin{itemize}
  \item English (fluent), French (beginner), Italian (beginner), Romanian (native)
\end{itemize}

\textbf{\textcolor{violet}{Music}} \\[-3.0ex]
\begin{itemize}
  \item Guitar
\end{itemize}

\textbf{\textcolor{violet}{Sports}} \\[-3.0ex]
\begin{itemize}
  \item polo, snowboarding, cycling
\end{itemize}

\textbf{\textcolor{violet}{Mind Sports}} \\[-3.0ex]
\begin{itemize}
  \item Poker (strategic tournament play), chess (club-level)
\end{itemize}




\end{document}